\documentclass[12pt]{book}

%These tell TeX which packages to use.
\usepackage{array,epsfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsxtra}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{eurosym}
\usepackage{times}
%Here I define some theorem styles and shortcut commands for symbols I use often
\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{cor}{Corollary}
\newtheorem*{rmk}{Remark}
\newtheorem{lem}{Lemma}
\newtheorem*{joke}{Joke}
\newtheorem{ex}{Example}
\newtheorem*{soln}{Solution}
\newtheorem{prop}{Proposition}

\newcommand{\lra}{\longrightarrow}
\newcommand{\ra}{\rightarrow}
\newcommand{\surj}{\twoheadrightarrow}
\newcommand{\graph}{\mathrm{graph}}
\newcommand{\bb}[1]{\mathbb{#1}}
\newcommand{\Z}{\bb{Z}}
\newcommand{\Q}{\bb{Q}}
\newcommand{\R}{\bb{R}}
\newcommand{\C}{\bb{C}}
\newcommand{\N}{\bb{N}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\m}{\mathbf{m}}
\newcommand{\MM}{\mathscr{M}}
\newcommand{\HH}{\mathscr{H}}
\newcommand{\Om}{\Omega}
\newcommand{\Ho}{\in\HH(\Om)}
\newcommand{\bd}{\partial}
\newcommand{\del}{\partial}
\newcommand{\bardel}{\overline\partial}
\newcommand{\textdf}[1]{\textbf{\textsf{#1}}\index{#1}}
\newcommand{\img}{\mathrm{omega}}
\newcommand{\ip}[2]{\left\langle{#1},{#2}\right\rangle}
\newcommand{\inter}[1]{\mathrm{int}{#1}}
\newcommand{\exter}[1]{\mathrm{ext}{#1}}
\newcommand{\cl}[1]{\mathrm{cl}{#1}}
\newcommand{\ds}{\displaystyle}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\cnt}{\mathrm{ct}}
\newcommand{\osc}{\mathrm{osc}}
\newcommand{\LL}{\mathbf{L}}
\newcommand{\UU}{\mathbf{U}}
\newcommand{\support}{\mathrm{support}}
\newcommand{\AND}{\;\wedge\;}
\newcommand{\OR}{\;\vee\;}
\newcommand{\Oset}{\varnothing}
\newcommand{\st}{\ni}
\newcommand{\wh}{\widehat}

%Pagination stuff.
\setlength{\topmargin}{-.3 in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textheight}{9.in}
\setlength{\textwidth}{6.5in}
\pagestyle{empty}

\begin{document}

\begin{center}
{\Large DATA 221 \\  Homework 1 }\\
\textbf{W. Trimble}\\ %You should put your name here
Due: Wednesday 2022-04-06 
\end{center}

\vspace{0.2 cm}

\subsection*{Reading:  MacKay Chapter 2 and 3}

\begin{enumerate}
\item\label{cheese}
[Problem 3.3 from Mackay, p.47]
Unstable particles are emitted from a source and decay at a distance x, a real number that has an exponential probability distribution with characteristic length $\lambda $. Decay events can be observed only if they occur in a window extending from x = 1 cm to x = 2 0 cm. N decays are observed at locations ${x_1, . . . , x_N }$. What is $\lambda$? 

% Here events have a probability of decay at distance $x$ proportional to $e^{-x/\lambda } $ where $\lambda$ can be called "characteristic length" or "mean length."


\item\label{breaths}
For concreteness, let us imagine our counter has observed six events, ${x_n} =  {1.5,2,3,4,5,12}$ 

Using a prior density that is proportional to ${d\lambda }\over {\lambda}$, find 
\begin{enumerate}
\item	The most likely value (MAP estimate) for $\lambda$? 
\item   A 95\% confidence interval for $\lambda$.
\end{enumerate}

Hint: this is a numerical integration problem.

\item\label{toscientific}
[Exercise 3.1 from MacKay p.47] 

A die is selected at random from three twenty-faced dice on which the symbols 1–10 are written with nonuniform frequency as follows.

\begin{tabular} {l c c c c c c c c c c c c c }
Symbol& 1& 2 &3 &4 &5 &6 &7 &8 &9 &10 \\
NumberoffacesofdieA& 6& 4 &3 &2 &1 &1 &1 &1 &1 &0  \\
NumberoffacesofdieB& 3 &3 &2 &2 &2 &2 &2 &2 &1 &1 \\
NumberoffacesofdieE& 2 &2 &2 &2 &2 &2 &2& 2& 2& 2 \\
\end{tabular}

A randomly chosen die is rolled 7 times, with the following outcomes: 5, 3, 9, 3, 8, 4, 7, 10.

\item What are the probabilities that the die is die A, B, or E?

\item\label{convert}

What does the zero probability for die A to return a 10 mean for inferences ? 

How many rolls on average would you need to establish 99:1 confidence between B and E? 

Hint: there is a theoretical answer (sums over things) and an attack by simulation.

\item
Reproduce the thre figures in Fig 2.1 and 2.3 in MacKay by downloading The Frequently Asked Questions Manual for Linux (or any other text with more than 30k words), splitting it into two-letter tokens, counting them, and presenting the histogram, its row-marginal and column-marginal variants as two-dimensional visualizations.  This particular graph is called a "Hinton diagram" but heatmaps or other symbol- or color- encodings are acceptable.

\item
Perform an eigenvalue decomposition of one of the 27 x 27 letter occurrence probability matrices.  Visualize an approximation to the matrix with all but the largest four eigenvectors discarded or set to zero alongside the original.



\end{enumerate}
\end{document}


